An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/intro.tex
intro

In this paper we present \app, the first automatic verification framework
for general software configurations. \app is based a collection of more powerful learning 
algorithms, that do not necessarily depend on templates. The learning process can be seen as a process of deriving  
a specification of configuration files, from a dataset containing a large sample of configuration files. In order to do that
we utilize a more sophisticated language model. Thus, in the first step \app analyzes the given dataset and generates a 
well-structured and probabilisticly-typed 
intermediate representation.

which aims to truly  achieve automatic configuration verification. we need to leverage a collection of more powerful learning 
algorithms, that do not necessarily depend on templates. In order to do that
there should be a more sophisticated language model, to which we would translate configuration files' entries.
Based on  the learned language model we would develop an abundant set of rules covering 
complex configuration errors. The set of learned rules should be accurate and we should be able to efficiently check 
the configuration files
of interest.

Based on the above argument, 
this paper presents \app, the first automatic verification framework
for general software configurations.
In particular, \app's workflow for verifying a given configuration file
can be viewed as a three-step methodology.
Firstly, \app analyzes a dataset containing sample configuration files,
thus generating a well-structured and probabilistically-typed 
intermediate representation.
Secondly, \app derives rules and constraints by analyzing
the intermediate representations, thus building a language model.
Finally, \app uses the resulting language model
to verify the given configuration file and detect potential errors.
Compared with previous efforts,
\app does not necessarily rely on users' templates 
and is capable of detecting tricky configuration errors that
cannot be identified by existing work (details in $\S$\ref{sec-motiv}).

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
Firstly, in order to formulate a correct language model, 
we need to infer each entry's type in a given configuration file, but 
the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt foo = MAX\_SIZE} is most likely
an integer rather than string; however, existing type inference 
work would report this is an error, because {\tt foo} should be assigned
an integer~\cite{zhang14encore}. \jon{Unclear what the error is. Be more precise} We address this problem by introducing 
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
a probabilistic type like 
{\tt \{foo, MAX\_SIZE, [(Int, 60\%), (String, 40\%)]\}}.
With such probabilistic types in hand,
we can generate a more accurate language model,
thus significantly improving our checking capability.

>>>>

In this paper we present \app, the first automatic verification framework
for general software configurations. \app is based on a collection of powerful learning 
algorithms, that do not necessarily depend on templates. The learning process takes as input a
 large sample of configuration files. The process is language-agnostic and it works for any type of configuration files, 
but all of the files in the sample need to be of the same type (such as  MySQL or httpd configuration files). From that sample
\app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules. One can see this learning process as a
way of deriving  
a specification for configuration files. The learning process works in two phases. In the first phase \app analyzes the given dataset and generates a 
well-structured and probabilisticly-typed 
intermediate representation. In the second phase \app derives rules and constraints by analyzing
the intermediate representations.  The set of learned rules is accurate and we are able to efficiently check 
the correctness of the configuration files
of interest and detect potential errors.
Compared with previous efforts,
\app does not necessarily rely on users' templates 
and is capable of detecting intricate configuration errors that
cannot be identified by existing work (details in $\S$\ref{sec-motiv}).

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
First, for variables of one types we learn different rules than for variables of different type. For example for integer variables $x$ and $Y$ we can learn that $X \leq Y$, while 
for strings we might want to learn a substring relation. We, therefore, first need to assign a type to every variable in a configuration file during the transformation phase.
However,
the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
Some of existing type inference 
work would report this is an error, because {\tt temp\_dir} should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
the following probabilistic type
{\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
Using the probabilistic types model,
we can generate a more accurate language model,
thus significantly improving our verification capabilities.
